How has the Brazilian Amazon been constructed as a problem? An analysis of

### 2022-04-09 Draft_April_2022/Full_draft_20220401.rmd
Updates to 4.3. section

@@

>>>>

Table 2, below, displays the multinational regression coefficients for the correlation between diverse problem constructions and locations. The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction. From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states. These findings indicate that constructing the Amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states. Additionally, pure sovereignty correlates in negative statistically significant ways to international settings in relation to conservation in Amazonian states. That is, constructing the Amazon as an issue of sovereignty is less likely in international settings than it is in Amazonian States. Interestingly, we see no statistically significant correlations between problem constructions in non-Amazonian states in relation to Amazonian states. This indicates that when presidents speak about the Amazon at the state level, constructions might be rather similar across different states. Furthermore, we also notice that some of the control variables correlate with some Amazonian problem constructions in interesting ways. For example, pure sovereignty constructions correlate negatively with election years in relation to conservation. That is, in election years conservation constructions are more likely to take place in comparison to sovereignty. As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation. This indicates that both deforestation increases and presidents are also more likely to construct the Amazon as an issue of economic integration.

@@

Putnam’s (1988) seminal article on the two level game between domestic and international politics analyzes how negotiations at both levels make policies possible. The author argues that both domestic and international levels need to be taken into consideration when analyzing how, often, domestic politics became entangled in international negotiations. The Amazon, as a region and a forest, has been the topic of international negotiations, national debates, and local policy implementation; though how the Amazon has been constructed as an issue differs on each of these three levels. While in Brasilia or internationally different presidents might construct the Amazon as an issue of conservation, the same presidents might construct the Amazon as an issue of economic integration or social development at the local level. This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” differ. The three level game entails that conservation might be a desirable construction when speaking internationally or in Brasilia about the Amazon, but not for local electorates. Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions about the issues the same policy addresses differ (see Alesina and Giuliano 2011).

More broadly, these correlations between different locations and problem constructions illustrate how expectations vary for diverse audiences. Whereas presidential discourses at the top matter to define and justify public policy (Zarefsky 2004), presidents shape their discourses according to who their audience might be and what the president expects that they want to hear. This democratic game may indeed contribute to the advancement of ambiguous, inefficient, or contradictory public policies from the outside to the Amazon, and from the inside out the Amazon. Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 (cite). During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … Such contradictory policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
